Global phase diagram and possible quantum spin liquid in the triangular $J$-$K$-$\Gamma$ model

### 2020-11-11 paper/paper.tex
Paper 2020-08-12 14:51

Geometric frustration, which arises when the lattice geometry gives rise to constraints that not every exchange bond can be simultaneously minimized in energy, plays an important role in various kinds of magnetic systems. The nearest-neighbor (NN) antiferromagetic (AFM) Heisenberg model on the triangular lattice is a typical example, once two of the spins on an elementary triangle are antiparallel to satisfy their antiferromagnetic interaction, the third one can no longer point in a direction opposite to both other spins. In particular, the spin-1/2 case has attracted numerous interests and was extensively studied after the seminal prediction by Anderson of a ``quantum spin liquid" (QSL) where a strong quantum fluctuation prevents any long-range order down to the zero temperature~\cite{Anderson1973}, although it has been shown by later studies that the ground state (GS) have a classical magnetic order with each spin on a triangle pointing to 120$^\circ$ with respect to each other~\cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}. When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a QSL state~\cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111,PhysRevLett.123.207203}. All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and give raise to a residual ground-state entropy. The spin-$1/2$ Kitaev model~\cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless QSL states supporting fractionalized excitations, is a celebrated example of a model with exchange frustration. In this model, the spins subject to the Kitaev interactions consisting of nearest neighbor Ising-type interactions, with the quantization axis depending on the spatial orientation of an exchange bond. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search for a solid-state realization of the Kitaev model. G. Khaliullin \emph{et al.,}~\cite{Khaliullin2005,PhysRevLett.102.017205} proposed that this highly anisotropic Kitaev interaction can be realized in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates A$_2$IrO$_3$ (A = Na, Li). In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbit coupling (SOC), electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra. However, in real materials, other types of interaction besides the Kitaev coupling are present, and these interactions may induce other interesting ordered and disordered phases. The simplest extension of the pure Kitaev model is the Heisenberg-Kitaev (HK) model~\cite{PhysRevLett.105.027204}, in which the NN Heisenberg interaction is also taken into account. This model has been extensively studied by various numerical methods~\cite{PhysRevLett.110.097204,PhysRevB.83.245104,PhysRevB.84.100406,PhysRevB.90.195102,PhysRevLett.119.157203}, which reveal the presence of four magnetically ordered phases with collinear spin patterns of ferromagnetic (FM), AFM, stripe, and zigzag types, besides extended spin-liquid phases near the Kitaev limits. Considering the most idealized crystal structure, another interaction beyond the HK model also must be included, i.e. bond dependent symmetric off-diagonal exchange, which is called the $\Gamma$ interaction~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}. Thus, the generic NN exchange Hamiltonian for the undistorted hexagonal compounds is the $J$-$K$-$\Gamma$ model, where the Heisenberg ($J$), Kitaev ($K$) and $\Gamma$ interactions are all included. Finite $\Gamma$ further enriches the phase diagram by adding non-collinear and incommensurate spiral phases~\cite{PhysRevLett.112.077204}. Moreover, in real materials, such as A$_2$IrO$_3$ and $\alpha$-RuCl$_{3}$, the dominant interactions are the $\Gamma$ and FM Kitaev terms which originate from both direct $d$-$d$ and anion mediated $d$-$p$ electron transfer, while the Heisenberg term has the smallest strength since it predominantly originates from the weak direct $d$-$d$ electron transfer~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/ModelDefinition.pdf}
    \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron. (b) The orientation of the cubic $x$, $y$, $z$ axes with respect to the octahedron. The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame. (c) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively. The different colors of the lattice sites label the four sublattices realizing the four sublattice transformation ( see main text for details).}
\end{figure}
In fact, magnetic ions located at the center of edge-sharing octahedra can not only form the honeycomb lattice but also the triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)), so the Kitaev and $\Gamma$ terms can naturally be generalized to the triangular lattice~\cite{PhysRevB.89.014414,PhysRevB.93.104417}. On the experimental side, studies of several classes of rare-earth compounds have recently shown that the quantum spin model on the triangular lattice can be formed by $4f$ moments. In particular, due to their possible Kramers doublets and spin-orbital coupling, the $4f$ electrons can be treated as $S_{eff}=1/2$ at low temperatures, and the spin-orbit entanglement can induce direction-dependent exchanges, such as the $K$ and $\Gamma$ terms. A typical example is YbMgGaO$_{4}$~\cite{srep16419,PhysRevLett.115.167203} and YbZnGaO$_{4}$~\cite{PhysRevLett.120.087201}, in which the Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra. More recently, an alternative family of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored. The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state~\cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,PhysRevB.100.241116,Liu_2018,PhysRevB.99.180401,PhysRevB.100.224417,PhysRevB.100.144432}. These triangluar magnets of rare-earth ions provide suitable platforms to study the interplay of geometric frustation and exchange frustration induced by spin-orbit coupling.

The phase diagram of the HK model ($\Gamma=0$) on the triangular lattice has been studied by means of Luttinger-Tisza minimization together with classical Monte Carlo simulation~\cite{PhysRevB.93.104417}, exact diagonalization (ED)~\cite{PhysRevB.91.155135,KaiLi2015}, and density matrix renormalization group~\cite{JPSJ.85.114710,PhysRevX.9.021017}. All these methods give consistent results about four magnetically ordered phases: two collinear patterns of FM and stripe types, and two noncollinear patterns of 120$^\circ$ N\'{e}el and noncoplanar spiral types. Note that the distortions of the 120$^\circ$ N\'{e}el order, when the model deviates from the AFM Heisenberg limit ($K=0$, $J>0$), were also called the $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417,PhysRevB.91.155135,JPSJ.85.114710}. However, the nature of the phase around the antiferromagnetic Kitaev point is still under debate. The Luttinger-Tisza minimization method suggested it to be a $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417}, the Schwinger-fermion mean-field theory proposed it to be a QSL~\cite{KaiLi2015}, while the density matrix renormalization group calculations suggested it to be a nematic phase~\cite{PhysRevB.91.155135,JPSJ.85.114710} or a stripe phase~\cite{PhysRevX.9.021017}. When the symmetric off-diagonal $\Gamma$ interaction is included, a classical analysis reveals that the stripe and ferromagnetic phases dominate the $J$-$K$-$\Gamma$ phase diagram, in addition to small regions of 120$^\circ$ N\'{e}el, $Z_{2}$ vortex crystal and nematic phases~\cite{PhysRevB.92.165108}. However, the studies on the effects of quantum fluctuations on the global $J$-$K$-$\Gamma$ phase diagram are scarce. In particular, since no exact solution has been reported so far for the pure spin-$1/2$ Kitaev and $\Gamma$ models on the triangular lattice, it also remains conceptually interesting to investigate whether QSL states could exist as possible GSs due to quantum fluctuations introduced by these exchange-frustrated interactions.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.95\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
    \caption{\label{fig:QuantumPhaseDiagram}(Color online) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model. The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively. There are in total ten phases including three FM phases denoted as FM-A, FM-B and FM-C, three stripe phases designated as Stripe-A, Stripe-B and Stripe-C, a modulated stripe phase, a 120$^\circ$ N\'{e}el phase, a dual N\'{e}el phase and a possible QSL phase. Phase boundaries are determined by the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ from ED calculations except for that depicted by the dashed line between the modulated stripe and stripe-B phases given by the classical analyses.}
\end{figure*}

@@

In the HK limit ($\Gamma=0$), as with the previous study~\cite{KaiLi2015}, we find five quantum phases. For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$, respectively. As mentioned in Sec.~\ref{sec:Model}, the HK model ($\Gamma=0$) preserves its form under the FST~\cite{PhysRevB.89.014414} but with different exchange interactions. Thus, by virtue of the FST, two more magnetic ordered phases can be identified. When $\beta=\pi - \arctan\frac{1}{2}$ in Eq.~\eqref{eq:FST}, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$, whose GS is a FM state. Therefore, transformating back to the original spin basis, a collinear stripe order can be obtained. Similarly, a noncollinear spiral order (Dual N\'{e}el) is obtained from the 120$^\circ$ N\'{e}el order for $\beta=-\arctan\frac{1}{2}$. However, for the phase containing the AFM Kitaev point ($J=\Gamma=0$, $K=1$), since it is mapped to itself under FST, we can not identify its magnetic properties with the FST.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/SpinConfigForPositiveGamma.pdf}
    \caption{\label{fig:GSForPositiveGamma}(Color online) Typical disordered GS for $J=K=0, \Gamma=1$. The 3D unit spin vectors were projected to the $xy$ plane and different vectors were represented by different colors.}
\end{figure}

@@

For pure negative $\Gamma$ model, we found several energetically degenerate states as the classcial GSs, including FM state, stripe states and a noncollinear state. The ordered moment of the FM state perpendicular to the lattice plane. As for the stripe states, there are three degenerate spin configurations as shown in Fig.~\ref{fig:GSForNegativeGamma}(a)-(c) and the moment directions for the cyan, red, pink, green, yellow and blue arrows are $[\bar{1}11]$, $[1\bar{1}\bar{1}]$, $[1\bar{1}1]$, $[\bar{1}1\bar{1}]$, $[11\bar{1}]$ and $[\bar{1}\bar{1}1]$, respectively. Apart from these collinear states, a noncollinear state also exist as the classical ground state. The magnetic unit-cell contains four lattice sites, and the moment directions for the yellow, gray, pink, cyan arrows in Fig.~\ref{fig:GSForNegativeGamma}(d) are $[11\bar{1}]$, $[111]$, $[1\bar{1}1]$ and $[\bar{1}11]$, respectively.
\begin{figure}
    \includegraphics[width=\columnwidth]{fig/SpinConfigForNegativeGamma.pdf}
    \caption{\label{fig:GSForNegativeGamma}(Color online) Typical classical GS spin configurations for $J=K=0, \Gamma=-1$. The 3D unit spin vectors were projected to the $xy$ plane and different vectors were represented by different colors. (a)-(c) Stripe ordered states. The directions for the cyan, red, pink, green, yellow and blue arrows are $[\bar{1}11]$, $[1\bar{1}\bar{1}]$, $[1\bar{1}1]$, $[\bar{1}1\bar{1}]$, $[11\bar{1}]$ and $[\bar{1}\bar{1}1]$, respectively. (d) Noncollinear state. The directions for the yellow, gray, pink, cyan arrows are $[11\bar{1}]$, $[111]$, $[1\bar{1}1]$ and $[\bar{1}11]$, respectively.}
\end{figure}

@@

The GSs for the classical antiferromagetic Kitaev model are also degenerate involving three types of nematic ordered states and three stripe ordered states. For the stripe ordered states shown in Fig.~\ref{fig:GSForPositiveK}(a)-(c), the corresponding ordered moments lie in the $yz$, $xz$ and $xy$ plane, respectively. For the nematic ordered state shown in Fig.~\ref{fig:GSForPositiveK}(d), the spins form antiferromagetic chains along the $x$-bond direction and the moment direction for the blue arrows are $[100]$. There are no association between different chains. Similarly, the antiferromagetic chains along the $y$-bond and $z$-bond direction for Fig.~\ref{fig:GSForPositiveK}(e) and Fig.~\ref{fig:GSForPositiveK}(f) respectively. The direction for the green arrows in Fig.~\ref{fig:GSForPositiveK}(e) and pink arrows in Fig.~\ref{fig:GSForPositiveK}(f) are $[010]$ and $[001]$, respectively.
\begin{figure}
    \includegraphics[width=\columnwidth]{fig/SpinConfigForPositiveKitaev.pdf}
    \caption{\label{fig:GSForPositiveK}(Color online) Classical nematic and stripe GS spin configurations for $J=\Gamma=0, K=1$.}
\end{figure}

>>>>

Geometric frustration, which arises when the lattice geometry gives rise to constraints that not every exchange bond can be simultaneously minimized in energy, plays an important role in various kinds of magnetic systems. The nearest-neighbor (NN) antiferromagetic (AFM) Heisenberg model on the triangular lattice is a typical example, once two of the spins on an elementary triangle are antiparallel to satisfy their antiferromagnetic interaction, the third one can no longer point in a direction opposite to both other spins. In particular, the spin-1/2 case has attracted numerous interests and was extensively studied after the seminal prediction by Anderson of a ``quantum spin liquid" (QSL) where a strong quantum fluctuation prevents any long-range order down to the zero temperature~\cite{Anderson1973}, although it has been shown by later studies that the ground state (GS) have a classical magnetic order with each spin on a triangle pointing to 120$^\circ$ with respect to each other~\cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}. When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a QSL state~\cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.94.121111,PhysRevB.96.075116,PhysRevLett.120.207203,PhysRevLett.123.207203}. All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and give raise to a residual ground-state entropy. The spin-$1/2$ Kitaev model~\cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless QSL states supporting fractionalized excitations, is a celebrated example of a model with exchange frustration. In this model, the spins subject to the Kitaev interactions consisting of nearest neighbor Ising-type interactions, with the quantization axis depending on the spatial orientation of an exchange bond. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search for a solid-state realization of the Kitaev model. G. Khaliullin \emph{et al.,}~\cite{Khaliullin2005,PhysRevLett.102.017205} proposed that this highly anisotropic Kitaev interaction can be realized in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates A$_2$IrO$_3$ (A = Na, Li). In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbital coupling (SOC), electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra. However, in real materials, other types of interaction besides the Kitaev coupling are present, and these interactions may induce other interesting ordered and disordered phases. The simplest extension of the pure Kitaev model is the Heisenberg-Kitaev (HK) model~\cite{PhysRevLett.105.027204}, in which the NN Heisenberg interaction is also taken into account. This model has been extensively studied by various numerical methods~\cite{PhysRevLett.110.097204,PhysRevB.83.245104,PhysRevB.84.100406,PhysRevB.90.195102,PhysRevLett.119.157203}, which reveal the presence of four magnetically ordered phases with collinear spin patterns of ferromagnetic (FM), AFM, stripe, and zigzag types, besides extended spin-liquid phases near the Kitaev limits. Considering the most idealized crystal structure, another interaction beyond the HK model also must be included, i.e. bond dependent symmetric off-diagonal exchange, which is called the $\Gamma$ interaction~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}. Thus, the generic NN exchange Hamiltonian for the undistorted hexagonal compounds is the $J$-$K$-$\Gamma$ model, where the Heisenberg ($J$), Kitaev ($K$) and $\Gamma$ interactions are all included. Finite $\Gamma$ further enriches the phase diagram by adding non-collinear and incommensurate spiral phases~\cite{PhysRevLett.112.077204}. Moreover, in real materials, such as A$_2$IrO$_3$ and $\alpha$-RuCl$_{3}$, the dominant interactions are the $\Gamma$ and FM Kitaev terms which originate from both direct $d$-$d$ and anion mediated $d$-$p$ electron transfer, while the Heisenberg term has the smallest strength since it predominantly originates from the weak direct $d$-$d$ electron transfer~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/ModelDefinition.pdf}
    \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron. (b) The orientation of the cubic $x$, $y$, $z$ axes with respect to the octahedron. The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame. (c) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively. The different colors of the lattice sites label the four sublattices realizing the four sublattice transformation ( see main text for details).}
\end{figure}
In fact, magnetic ions located at the center of edge-sharing octahedra can not only form the honeycomb lattice but also the triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)), so the Kitaev and $\Gamma$ terms can naturally be generalized to the triangular lattice~\cite{PhysRevB.89.014414,PhysRevB.93.104417}. On the experimental side, studies on several classes of  compounds containing localized $4d$, $5d$ or $4f$ electrons have recently shown that the quantum spin model on the triangular lattice can be formed by the localized moments~\cite{PhysRevB.86.140405,PhysRevB.94.174410,srep16419,PhysRevLett.115.167203,PhysRevLett.120.087201}. In particular, due to their possible Kramers doublets and spin-orbital coupling, these moments can be treated as $S_{eff}=1/2$ at low temperatures, and the spin-orbital entanglement can induce direction-dependent exchanges, such as the $K$ and $\Gamma$ terms. A typical example is YbMgGaO$_{4}$~\cite{srep16419,PhysRevLett.115.167203}, in which the Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra. More recently, an alternative family of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored. The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state~\cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,PhysRevB.100.241116,Liu_2018,PhysRevB.99.180401,PhysRevB.100.224417,PhysRevB.100.144432}. These triangluar magnets provide suitable platforms to study the interplay of geometric frustation and exchange frustration induced by spin-orbital couplings.

The phase diagram of the HK model ($\Gamma=0$) on the triangular lattice has been studied by means of Luttinger-Tisza minimization together with classical Monte Carlo simulation~\cite{PhysRevB.93.104417}, exact diagonalization (ED)~\cite{PhysRevB.91.155135,KaiLi2015}, and density matrix renormalization group~\cite{JPSJ.85.114710,PhysRevX.9.021017}. All these methods give consistent results about four magnetically ordered phases: two collinear patterns of FM and stripe types, and two noncollinear patterns of 120$^\circ$ N\'{e}el and noncoplanar spiral types. Note that the distortions of the 120$^\circ$ N\'{e}el order, when the model deviates from the AFM Heisenberg limit ($K=0$, $J>0$), were also called the $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417,PhysRevB.91.155135,JPSJ.85.114710,PhysRevResearch.1.013002}. However, the nature of the phase around the antiferromagnetic Kitaev point is still under debate. The Luttinger-Tisza minimization method suggested it to be a $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417}, the Schwinger-fermion mean-field theory proposed it to be a QSL~\cite{KaiLi2015}, the Schwinger-boson mean-field theory thought it to be a nematic phase~\cite{PhysRevB.95.024421}, while the density matrix renormalization group calculations suggested it to be a nematic phase~\cite{PhysRevB.91.155135,JPSJ.85.114710} or a stripe phase~\cite{PhysRevX.9.021017}. When the symmetric off-diagonal $\Gamma$ interaction is included, a classical analysis reveals that the stripe and ferromagnetic phases dominate the $J$-$K$-$\Gamma$ phase diagram, in addition to small regions of 120$^\circ$ N\'{e}el, $Z_{2}$ vortex crystal and nematic phases~\cite{PhysRevB.92.165108}. However, the studies on the effects of quantum fluctuations on the global $J$-$K$-$\Gamma$ phase diagram are scarce. In particular, since no exact solution has been reported so far for the pure spin-$1/2$ Kitaev and $\Gamma$ models on the triangular lattice, it also remains conceptually interesting to investigate whether QSL states could exist as possible GSs due to quantum fluctuations introduced by these exchange-frustrated interactions.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.95\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
    \caption{\label{fig:QuantumPhaseDiagram}(Color online) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model. The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively. There are in total ten phases including three FM phases denoted as FM-A, FM-B and FM-C, three stripe phases designated as Stripe-A, Stripe-B and Stripe-C, a modulated stripe phase, a 120$^\circ$ N\'{e}el phase, a dual N\'{e}el phase and a possible QSL phase. Phase boundaries are determined by the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ from ED calculations except for that depicted by the dashed line between the modulated stripe and stripe-B phases given by the classical analyses. The inset sub-figure(a) is the global phase diagram of the HK model. The two-way arrows indicate parameter pairs that can be connected by the FST.}
\end{figure*}

@@

In the HK limit ($\Gamma=0$), as with the previous study~\cite{KaiLi2015}, we find five quantum phases. For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$, respectively. As mentioned in Sec.~\ref{sec:Model}, the HK model ($\Gamma=0$) preserves its form under the FST~\cite{PhysRevB.89.014414} but with different exchange interactions. Thus, by virtue of the FST, two more magnetic ordered phases can be identified. For the FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$ whose GS is a FM state, the FST maps it to a Heisenberg-Kitaev model of the original spin operators $\bm{S}$ with $\beta=\pi - \arctan\frac{1}{2}$. Accordingly, the FM state of $\bm{S}^{\prime}$ is transformed to a collinear stripe state of $\bm{S}$. Similarly, the AFM Heisenberg model of $\bm{S}^{\prime}$ is also mapped to a Heisenberg-Kitaev model of $\bm{S}$ with $\beta=-\arctan\frac{1}{2}$ and the 120$^\circ$ N\'{e}el state of $\bm{S}^{\prime}$ is transformed to a noncollinear spiral order (Dual N\'{e}el) of $\bm{S}$. However, for the phase containing the AFM Kitaev point ($J=\Gamma=0$, $K=1$), since it is mapped to itself under FST, we can not identify its magnetic properties with the FST.

% When $\beta=\pi - \arctan\frac{1}{2}$ in Eq.~\eqref{eq:FST}, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$, whose GS is a FM state. Therefore, transformating back to the original spin basis, a collinear stripe order can be obtained. Similarly, a noncollinear spiral order (Dual N\'{e}el) is obtained from the 120$^\circ$ N\'{e}el order for $\beta=-\arctan\frac{1}{2}$. However, for the phase containing the AFM Kitaev point ($J=\Gamma=0$, $K=1$), since it is mapped to itself under FST, we can not identify its magnetic properties with the FST.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/SpinConfigForPositiveGamma.pdf}
    \caption{\label{fig:GSForPositiveGamma}(Color online) Typical disordered GS for $J=K=0, \Gamma=1$. For clarity, the equal spin vectors are marked with the same color, and the arrows denote the projections of the three-dimensional vectors to the $xy$ plane.}
\end{figure}

@@

For pure negative $\Gamma$ model, we found several energetically degenerate states as the classcial GSs, including FM state, stripe states and a noncollinear state. The ordered moment of the FM state perpendicular to the lattice plane. As for the stripe states, there are three degenerate spin configurations as shown in Fig.~\ref{fig:GSForNegativeGamma}(a)-(c) and the moment directions for the cyan, red, pink, green, yellow and blue arrows are $[\bar{1}11]$, $[1\bar{1}\bar{1}]$, $[1\bar{1}1]$, $[\bar{1}1\bar{1}]$, $[11\bar{1}]$ and $[\bar{1}\bar{1}1]$, respectively. Apart from these collinear states, a noncollinear state also exist as the classical ground state. The magnetic unit-cell contains four lattice sites, and the moment directions for the yellow, gray, pink, cyan arrows in Fig.~\ref{fig:GSForNegativeGamma}(d) are $[11\bar{1}]$, $[111]$, $[1\bar{1}1]$ and $[\bar{1}11]$, respectively.
\begin{figure}
    \includegraphics[width=\columnwidth]{fig/SpinConfigForNegativeGamma.pdf}
    \caption{\label{fig:GSForNegativeGamma}(Color online) Typical classical GS spin configurations for $J=K=0, \Gamma=-1$. The spin vectors were projected to the $xy$ plane and different vectors were represented by different colors. (a)-(c) Stripe ordered states. The directions for the cyan, red, pink, green, yellow and blue arrows are $[\bar{1}11]$, $[1\bar{1}\bar{1}]$, $[1\bar{1}1]$, $[\bar{1}1\bar{1}]$, $[11\bar{1}]$ and $[\bar{1}\bar{1}1]$, respectively. (d) Noncollinear state. The directions for the yellow, gray, pink, cyan arrows are $[11\bar{1}]$, $[111]$, $[1\bar{1}1]$ and $[\bar{1}11]$, respectively.}
\end{figure}

@@

The GSs for the classical antiferromagetic Kitaev model are also degenerate involving three types of nematic ordered states and three stripe ordered states. For the stripe ordered states shown in Fig.~\ref{fig:GSForPositiveK}(a)-(c), the corresponding ordered moments lie in the $yz$, $xz$ and $xy$ plane, respectively. For the nematic ordered state shown in Fig.~\ref{fig:GSForPositiveK}(d), the spins form antiferromagetic chains along the $x$-bond direction and the moment direction for the blue arrows are $[100]$. Different antiferromagnetic chains are decoupled in the nematic state. Similarly, the antiferromagetic chains along the $y$-bond and $z$-bond direction for Fig.~\ref{fig:GSForPositiveK}(e) and Fig.~\ref{fig:GSForPositiveK}(f) respectively. The direction for the green arrows in Fig.~\ref{fig:GSForPositiveK}(e) and pink arrows in Fig.~\ref{fig:GSForPositiveK}(f) are $[010]$ and $[001]$, respectively.
\begin{figure}
    \includegraphics[width=\columnwidth]{fig/SpinConfigForPositiveKitaev.pdf}
    \caption{\label{fig:GSForPositiveK}(Color online) Classical stripe and nematic GS spin configurations for $J=\Gamma=0, K=1$. (a)-(c) Stripe states. (d)-(f) Nematic states.}
\end{figure}
